---
title: "Final"
author: "Kevin Deng"
date: "December 10, 2017"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Drugs
1. Among the capacity levels of 30K, 35K, 40K, 45K, 50K, 55K, and 60K units, which level maximize expected profit?
```{r}
rm(list=ls())
set.seed(1234)
# Build a model to calculate profit
profit_model <- function(cap){
  profit = 0
  for (i in 1:10){
    x = round(rnorm(n = 1, mean = 50000, sd = 12000))
    if (i == 1){
      if (x >= cap){
      cost <- 16 * cap + 0.2 * cap + 0.4 * cap
      profit <- 3.7 * cap - cost
      }
      else{
      cost <- 16 * cap + 0.2 * x + 0.4 * cap
      profit <- 3.7 * x - cost
      }
    }
    else{
      if (x >= cap){
      cost <- 0.2 * cap + 0.4 * cap
      profit <- profit + 3.7 * cap - cost
      }
      else{
      cost <- 0.2 * x + 0.4 * cap
      profit <- profit + 3.7 * x - cost
      }
    }
  }
  return(profit)
}

Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}

# Run a loop to see the average profit for each level of capacity
profit1 <- rep(0, 1000)
profit2 <- rep(0, 1000)
profit3 <- rep(0, 1000)
profit4 <- rep(0, 1000)
profit5 <- rep(0, 1000)
profit6 <- rep(0, 1000)
profit7 <- rep(0, 1000)
for (i in 1:1000){
  # Capacity of 30K
  capacity <- 30000
  profit1[i] <- profit_model(capacity)
  # Capacity of 35K
  capacity <- 35000
  profit2[i] <- profit_model(capacity)
  # Capacity of 40K
  capacity <- 40000
  profit3[i] <- profit_model(capacity)
  # Capacity of 45K
  capacity <- 45000
  profit4[i] <- profit_model(capacity)
  # Capacity of 50K
  capacity <- 50000
  profit5[i] <- profit_model(capacity)
  # Capacity of 55K
  capacity <- 55000
  profit6[i] <- profit_model(capacity)
  # Capacity of 60K
  capacity <- 60000
  profit7[i] <- profit_model(capacity)
}
Mode(profit1)
Mode(profit2)
Mode(profit3)
Mode(profit4)
Mode(profit5)
Mode(profit6)
Mode(profit7)
maximized = 50000
capacities <- c(30000, 35000, 40000, 45000, 50000, 55000, 60000)
expprofit <- c(Mode(profit1), Mode(profit2), Mode(profit3), Mode(profit4), Mode(profit5), Mode(profit6), Mode(profit7))
plot(capacities, expprofit, abline(v = maximized, lty = 2))

```
After running my model for 1000 times, the level of 50K units per year is the level maximizing expected profit.

2. Using the capacity from previous question, NuFeel can be 95% certain that expected profit for the 10-year period will be between what two values?
```{r}
# Buile a confidence interval function
confi_interval <- function(x, level){
  if (level == 0.99){
    interval <- c((mean(x)-2.58*(sd(x))),(mean(x)+2.58*(sd(x))))
    }
  if (level == 0.95){
    interval <- c((mean(x)-1.96*(sd(x))),(mean(x)+1.96*(sd(x))))
    }
  if (level == 0.90){
    interval <- c((mean(x)-1.65*(sd(x))),(mean(x)+1.965*(sd(x))))
    }
  return(interval)
}
interval <- confi_interval(profit5, 0.95)
sprintf('Thus, the two values will be [%s, %s]', interval[1], interval[2])
```

## Warranty

```{r}
rm(list = ls())
set.seed(1234)
# Build three empty vectors
totalFailures <- rep(0, 1000)
totalCost <- rep(0, 1000)
totalDevices <- rep(0, 1000)
for (k in 1:1000){
  x <- c(1:6)
  y <- pgamma(x, 2, rate = 2)
  # set broken[1] = 0, so it would not the warranty year at first in line 135
  broken <- rep(0,7)
  # As I bought 1 device at first, so I need to set my cost to 100
  cost <- 100
  warranty <- rep(0, 6)
  count <- 1
  for (i in 1:length(x)){
    if (x[i] <= 1 + broken[i] * x[i]){
      broken[i+1] <- rbinom(1, 1, y[count])
      if (broken[i+1] == 1){
        warranty[i] <- 1
        count = 1
      }
      else{
        count = count + 1
      }
    }
    else{
      broken[i+1] <- rbinom(1, 1, y[count])
      cost <- cost + 100*broken[i+1]
      count <- count + 1
    }
  }
  totalFailures[k] <- sum(warranty)
  totalCost[k] <- cost
  totalDevices[k] <- sum(broken) + 1
}
par(mfrow = c(3,1))
hist(totalCost, breaks = 100); hist(totalFailures, breaks = 100); hist(totalDevices, breaks = 100)
par(mfrow = c(1,1))
mean(totalCost)
mean(totalFailures)
mean(totalDevices)

```
3.
After I ran 1000 times of my model, the total cost is $226.2

4. 
After I ran 1000 times of my model, the number of failures during the warranty period is 3.124

5. 
After I ran 1000 times of my model, the number of devices owned is 5.386

## Clearance
6. How many days will it take for WTF to sell all 12 washers?
```{r}
rm(list=ls())
# set seed to make sure my outcome doesn't change every time the model was run
set.seed(1234)
customers <- c(0, 1, 2, 3, 4)
prob1 <- c(0.15, 0.25, 0.30, 0.20, 0.10)
# Build a discrete distribution model
drnd <- function(x, p, n) {
    z <- NULL
    ps <- cumsum(p)
    r <- runif(n)
    for (i in 1:n){
      z <- c(z, x[which(r[i] <= ps)[1]])
    }
    return(z)
}

# Build the Mode function to find the most frequent value in a list
Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}

prob2 <- c(0.4, 0.25, 0.35)
days <- rep(0, 1000)
for (k in 1:1000){
  washers <- c(0, 0, 0)
  for (day in 1:100){
    # Use the model to get the number of cusomers arriving every day
    out <- drnd(customers, prob1, 1)
    # Calculate the number of customers who are interested in sale-priced items
    intersted_customers <- rbinom(1, out, 0.6)
    for (i in 1:intersted_customers){
    ps <- cumsum(prob2)
    r <- runif(1)
      for (j in 1:3){
        if (r <= ps[j]){
          washers[j] = washers[j] + 1
          break
        }
      }
    }
  # To prevent WTF from selling more than 5
    if (washers[1] >= 5){
      washers[1] = 5
    }
    if (washers[2] >= 3){
      washers[2] = 3
    }
    if (washers[3] >= 4){
      washers[3] = 4
    }
    # When all three machines were sold out
    if (washers[1] >= 5 && washers[2] >= 3 && washers[3] >= 4){
      break
    }
  }
  days[k] <- day
}
Mode(days)
hist(days, breaks = 100, xlim=range(5:25))
```
After running my model for 1000 times, I found that it takes 9 days to sell all the washers.

## Waiting Room
7. Compute the sample mean and standard deviation for this data.
```{r}
rm(list=ls())
completiontime <- c(8, 12, 26, 10, 23, 21, 16, 22, 18, 17, 36, 9)
mean(completiontime)
sd(completiontime)
```
Thus, the sample mean is 18.16667 and the sample standard deviation is 8.110973

8. Construct a 99% confidence interval for the population mean interview time.
```{r}
confi_interval <- function(x, level, n){
  if (level == 0.99){
    interval <- c((mean(x)-2.58*(sd(x)/(n^0.5))),(mean(x)+2.58*(sd(x)/(n^0.5))))
    }
  if (level == 0.95){
    interval <- c((mean(x)-1.96*(sd(x)/(n^0.5))),(mean(x)+1.96*(sd(x)/(n^0.5))))
    }
  if (level == 0.90){
    interval <- c((mean(x)-1.65*(sd(x)/(n^0.5))),(mean(x)+1.65*(sd(x)/(n^0.5))))
    }
  return(interval)
}

confi_interval(completiontime, 0.99, 12)
```
So a 99% confidence interval would be [12,12576, 24.20757]

9. How large a sample is required to obtain a 99% confidence interval whose accuracy is within +/- 8 minutes?
```{r}
N = 2.58^2*sd(completiontime)^2/(8^2)
round(N)
```
So the sample should be 7.

## Scenarios
10. Making a forecast about future to gather useful insights based on every scenario might sounds awesome. However, if we only consider some scenarios instead of every scenario to make a forecast, we would have following advantages:
  1. Preventing our forecasting model from being overfitting. As we add more and more variables to our model, our model might have more chances to become overfitting.
  2. Reducing the cost of collecting information.
  3. Saving a lot of time of collecting information and building forecast model.
  
## Multiple Choice
11. c

12. a

13. b

14. c

15. c

16. d

17. d

## Short Answer in R
18. 
```{r}
pnorm(q = 460, mean = 480, sd = 10, lower.tail = T)
```
The probability that any container is under 460 grams would be 2.275%

19. 
Y = X1 + X2
```{r}
Ex = 460 + 460
SD = (100 + 100 + 2*10*10*0.77)^0.5
Ex
SD
```

The expected total weight is 920
The standard deviation is 18.81489

20.
```{r}
pnorm(q = 920, mean = 920, sd = SD, lower.tail = T)
```
The probability that a total weight of a duo-pack is under 920 grams is 50%

21.
```{r}
x = 460 + 1.96*(10)
x
```
It should be 479.6 grams.

